\documentclass[11pt]{article}
\usepackage{jeffe,handout}

% =========================================================
\begin{document}

\headers{CS 150}{Programming Assignment 7 (due December 8 by
11:59pm)}{Fall 2008}

\begin{center}
\LARGE \textbf{CS 150: Intro to OOP, Fall 2008}
\\
\textbf{Programming Assignment 7}
\\[1ex]
\Large Due \emph{via email} by 11:59pm on December 8, 2008\\

\end{center}

%----------------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In this assignment, we will be redoing the first program which used
the cs1graphics package.  In addition to ALL of the requirements on
that assignment, you will incorporate several other elements in the
program.

\begin{itemize}
\item Use your animal class from programming assignment 4 somewhere
in your program.  If your animal class did not work, you must fix
it!  I gave comments about what was wrong in the files I sent out,
and you can stop by my office if you need more detailed comments
about what to fix.  Use all of the methods you designed in this
class somewhere in your program.

\item Use at least one loop to animate an animal or object moving on
the screen.  (Repeated sleep statements are poor programming form,
so use loops instead where ever possible.)

\item In general, since we know so much more now, you should be able
to fix up many things from your first program.  Try to have fun with
this!

\end{itemize}

In your email submission, include all files necessary to run your
program.  As always, make sure to include comments in your program.

\end{document}
