\documentclass[11pt]{article}
\usepackage{jeffe,handout}

% =========================================================
\begin{document}

\headers{CS 150}{Programming Assignment 4 (due March 18,
2009)}{Sprint 2009}

\begin{center}
\LARGE \textbf{CS 150: Intro to OOP, Fall 2008}
\\
\textbf{Programming Assignment 4}
\\[1ex]
\Large Due \emph{via email} by 11:59pm on Wednesday, March 18, 2009\\

\end{center}

For this assignment, you must work individually.  As usual, you are
welcome to discuss {\em general} python syntax, but your design and
coding should all be done individually.  Please refer to the class
syllabus or consult the instructor if you have any questions.

\begin{problems}
%----------------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item Exercises 6.15 and 6.16

Please submit both class definitions (one called Set for 6.15 and one called SortedSet for
6.16) in a file called myset.py.  

Some things to keep in mind:

\begin{itemize}

\item I expect your sets to be able to support any string or numeric value being added.

\item Make sure to use comments and meaningful variable names throughout the classes.

\item It might be helpful to write a \_\_str\_\_ method for your Set class, also, so that you can test that your code is working.

\item Remember to test your code!  Import your classes in python, create several sets and sorted sets, and add/remove numbers and strings to them to see if everything is added correctly and with no duplicates.  

\end{itemize}

\item Extra Credit: Write the following methods for either your Set or your SortedSet class:

\begin{enumerate}
\item Implement an \_\_add\_\_ function (overloading $+$) which takes two sets and returns
the union of them in a new set.

\item Implement an \_\_eq\_\_ function (overloading $==$) which take two sets and returns
True if the sets are the same.

\item Implement an xor(self, other) function, which will be called by
set1.xor(set2).  The function should return  all elements which are
either in set1 or in set2 (but NOT in both).
\end{enumerate}

\end{problems}
\end{document}
