\documentclass[11pt]{article}
\usepackage{jeffe, handout}
\hidesolutions

\setlength{\headsep}{0.5in}

% ======================================================================
\begin{document}

%\thispagestyle{empty}

\headers{CS314: Algorithms}{Homework 2 (due 2/12/09}{Spring 2009}

\begin{center}
{\LARGE\bf      CS314: Algorithms}
\\[1ex]
{\Large\bf      Homework 2, due Thursday, February 12}
\\[0.25in]
\end{center}

%----------------------------------------------------------------------
This homework will be graded by oral presentations to the teacher.
There will be a sign-up sheet in class on Monday, Feb. 9; you will
be asked to pick a half hour spot sometime on Thursday for your
group to meet with the instructor.  Be sure to check your schedule
(and that of your partner, if you have one) so that you have several
options for when to meet ready to go.

You can still submit homework in pairs; you will just alternate
problems to present with your partner.  Please see the homework page
on the course website regarding oral presentation format and
suggestions.

As always, when asked to design an algorithm, you must also include
a proof of correctness and running time for that algorithm. In
particular, if the problems asks you to design an algorithm with a
particular run time, you must still analyze {\em your} algorithm to
prove that it meets that running time.

\medskip
\bigskip\hrule\bigskip

\section*{Required Problems}

% ======================================================================
\begin{problems}
\item Chapter 6, problem 1

\item Chapter 6, problem 2

\item Chapter 6, problem 5

\item Chamber6, problem 7

\end{problems}

\end{document}
